workshop

### 2023-02-20 scripts/workshop/workshop.Rmd
change bin width

```{r}
comm_data %>% ggplot(.,aes(x=size)) + geom_histogram() + labs(title = "Untransformed abundance")
comm_data %>% ggplot(.,aes(x=log10(size))) + geom_histogram() + labs(title = "log10-transformed abundance")
comm_data %>% ggplot(.,aes(x=cc)) + geom_histogram() + labs(title = "Untransformed cc")
comm_data %>% ggplot(.,aes(x=log10(cc))) + geom_histogram() + labs(title = "log10-transformed cc")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC)) + geom_histogram() + labs(title = "Mean Water Temp")
```

>>>>

```{r}
comm_data %>% ggplot(.,aes(x=size)) + geom_histogram() + labs(title = "Untransformed abundance")
comm_data %>% ggplot(.,aes(x=log10(size))) + geom_histogram() + labs(title = "log10-transformed abundance")
comm_data %>% ggplot(.,aes(x=cc)) + geom_histogram() + labs(title = "Untransformed cc")
comm_data %>% ggplot(.,aes(x=log10(cc))) + geom_histogram() + labs(title = "log10-transformed cc")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC)) + geom_histogram(binwidth=2) + labs(title = "Mean Water Temp")
```
